Machine learning high multiplicity matrix elements for electron-positron and hadron-hadron colliders

### 2023-03-13 paper2.tex
add process in figure caption

\begin{figure}
    \includegraphics[width=\linewidth]{fame2/5j_cross_sections.pdf}
    \caption{Scatter plot showing the variation in predictions of
    the 5 jet total cross-section for the 20 replica models, where
    the plotted cross-section is normalised by the truth value
    provided by {\MadGraph}.
    Total cross-sections in each subplot are evaluated at the
    renormalisation scale quoted in the upper right.
    The mean prediction of the 20 replica models is drawn as the horizontal
    blue line with one standard deviation illustrated by the blue band.
    The total cross-section as predicted by {\MadGraph} is plotted
    as the horizontal black line.}
    \label{fig:1L_5j_cs}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{fame2/5j_cross_sections.pdf}
    \caption{Scatter plot showing the variation in predictions of
    the $e^{+}e^{-} \rightarrow q\bar{q}ggg$ total cross-section for the 20 replica models, where
    the plotted cross-section is normalised by the truth value
    provided by {\MadGraph}.
    Total cross-sections in each subplot are evaluated at the
    renormalisation scale quoted in the upper right.
    The mean prediction of the 20 replica models is drawn as the horizontal
    blue line with one standard deviation illustrated by the blue band.
    The total cross-section as predicted by {\MadGraph} is plotted
    as the horizontal black line.}
    \label{fig:1L_5j_cs}
\end{figure}
